---
title: "PT"
author: "Maksym Hudymenko"
date: "`r Sys.Date()`"
output: html_document
---
Content

Best Selling Music Artists of All Time

About Dataset
The following list of best-selling music artists includes those music acts from the 20th century to the present with claims of 75 million or more record sales worldwide.

COLUMN DESCRIPTION
'Artist' : Name of the artist
'Country' : Country from where the artist is from
'period_active' : Time when the artists made their music
'Year' : Release year of their first chartered record
'Genre' : Genre of the artist's music
'TCU' : Total Certified Units
'Sales' : Claimed sales of the records
FILE INFORMATION
File: 'best _selling _artists.csv'
The file contains the following columns:

'Artist' : Name of the artist
'Country' : Country from where the artist is from
'period_active' : Time when the artists made their music
'Year' : Release year of their first chartered record
'Genre' : Genre of the artist's music
'TCU' : Total Certified Units
'Sales' : Claimed sales of the records

https://www.kaggle.com/datasets/kabhishm/best-selling-music-artists-of-all-time?resource=download


```{r}
setwd("C:/Users/USER/Desktop/DataProcessingLabs/PT")
data <- read.csv("best_selling_artists.csv")
head(data)
```
```{r}
tail(data)
```
```{r}
subset(data, Country == "Barbados")
```

```{r}
mean(data$Year)
```

```{r}
sd(data$Year)
```

```{r}
var(data$Year)
```

```{r}
plot(data$Year, main = "Main Plot")
hist(data$Year, main = "Histogram")
h1 <- hist(data$Year, main = "Histogram & Polygon")
lines(h1$counts ~ h1$mids, col = "red")
boxplot(data$Year, main = "Boxplot")
```